### 2015-01-09 paper/Content/03conclusion.tex
Conclusion

\IEEEPARstart{U}{sing} this approach is the future of Android and makes everything better. That is because we are such cool guys and we'll become scientists in the next two years. Here are other good reasons:

	\subsection{Outlook of our approach}

	\subsection{Other people active in this context}

>>>>

\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} Framework and have identified 
principle components which are generally used for developing an \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
Applying MVP offers various benefits like a better testability [……], but the paper has shown that it is often hard to define the roles 
of the \emph{Android} components considering MVP and to embed those components into the whole MVP model. But finally we can offer an MVP approach 
for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.

However, just the essential framework components have been examined regarding their MVP compatibility and used in the prototype. 
The MVP pattern for \emph{Android} would only succeed in practice if a wide bandwidth of framework components was adaptable. 
In course of additional research studies addressing this topic we recommend to examine further frameworks components and 
evaluate them regarding their MVP compatibility by implementing prototypes.

There are further and particularly similar MVP approaches developed and provided by the \emph{Android} developer community. 
\emph{Google} developer \emph{Chris Banes} has developed the \emph{Android} app \emph{philm} basing on MVP. 
The very demonstrative source code is offered on \emph{github} [https://github.com/chrisbanes/philm] and worth seeing. 
Moreover there is a huge developer community on \emph{Google+} [https://plus.google.com/communities/114285790907815804707] dealing with different MVP approaches. 
Finally, we want to draw your attention to the paper \emph{Android Passive MVC: a Novel Architecture Model for Android Application Development} 
[Quelle] which is worth reading and has been an inspiration for our approach. Although the paper proposes an architecture which is rather MVC than MVP-based, 
it offers an interesting approach how the components of an \emph{Android} app can be organized for building an MV-x structure.
